Opt-K

### 2013-03-13 paper/paper.tex

One challenge is how to model the volume of states which are at the
``edge'' of the model. Is the volume of these states infinite, extending
all the way out to infinity in some direction? This seems problematic.
Instead, it seems appropriate to assert that the volume is bounded by
the convex hull of the data. That is, the volume of a state might be defined
as the volume of the intersection of its Voronoi cell and the convex
hull of the dataset.

Instead, we use a slightly modified version of this definition that adopts
the same spirit. Instead of taking the outer bounding region to be the convex
hull of the data, we take it to be the set of all trail points such that the nearest neighbor of the trial point within the dataset is less than a certain
cutoff, $R$. This can be computed relatively efficiently using a BallTree data
structure. For further efficiency, we might use only a random subsample of the
dataset for this nearest neighbor computation.

>>>>

One challenge is how to model the volume of states which are at the
``edge'' of the model. Is the volume of these states unbounded, given that they extend all the way out to infinity in some direction? This would be problematic.
It seems appropriate to assert that the volume of these edge states is bounded in some way by the extent of our dataset. For example, the volume of a state might be defined as the volume of the intersection of its Voronoi cell and the convex hull of the whole dataset.

We use a slightly modified version of this definition that adopts
the same spirit. Instead of taking the outer bounding region to be the convex hull of the data, we take it to be the set of all trial points such that the nearest data point to the trial point is closer than a certain cutoff, $R$. This can be computed relatively efficiently using a BallTree data structure. For further efficiency, we might use only a random subsample of the dataset for this nearest neighbor computation.
